---
title: "PROJECT"
author: "KANDULA NAVEEN KUMAR - 17MIS1056"
date: "01/05/2021"
output: word_document
---

```{r}
rm(list = ls())
```

```{r}
data <- read.csv("D:\\8TH SEM\\project\\Train.csv")
data
```


#Structure And Summary Of The Data
```{r}
str(data)
```

```{r}
summary(data)
```

#Customer Gender Visualization
```{r}
gender <- table(data$Gender)
barplot(gender,main = "Gender Comparison",xlab = "Gender",ylab = "Count",col=c("pink","lightblue"))

```



#Visualization of Age Distribution
```{r}
hist(data$Age,col = "lightblue",main = "Hitogram to show count of Age Class",xlab = "Age Class",ylab = "Frequency",labels = TRUE)

```

```{r}
boxplot(data$Age,col = "#ff0066",main="Boxplot for Descriptive Analysis of Age")
```

```{r}
library(plotrix)
```

```{r}
pct = round(gender/sum(gender)*100)
lbs = paste(c("Female","Male")," ",pct,"%",sep = " ")
```


```{r}
pie3D(gender,labels = lbs,main="Pie Chart Showing Ratio Of Female And Male",col = c("red","orange"))

```

#simplify the dataset

```{r}
data <- data[,2:9]

```

```{r}
summary(data)
str(data)
```

```{r}
unique(data$Profession)
```


#transforming blanks into NA's
```{r}
data[data==""]<-NA
data<-data[complete.cases(data),]
```

```{r}
library(dplyr)
```


```{r}
dataset <-data %>% select_if(is.numeric)

character <- data %>% select_if(is.character)
```


# Transforming character into numerical/dummy

```{r}
library(fastDummies)

character <-dummy_cols(character,remove_most_frequent_dummy = TRUE)
```

```{r}
#dataset <- cbind(dataset,character[6:18])
#dataset
```

```{r}
library(factoextra)
```

```{r}
library(purrr)
set.seed(123)
iss <- function(k){
  kmeans(dataset,k,iter.max = 100,nstart = 100,algorithm = "Lloyd")$tot.withinss
}

k.values <- 1:10

iss_values <- map_dbl(k.values,iss)
plot(k.values,iss_values,type = "b",pch=19,frame=FALSE,xlab = "Number Of Clusters K",ylab = "Total Intra Clusters Sum Of Squares",col="#1287A5")
```

```{r}
fviz_nbclust(dataset,kmeans,method = "silhouette")
```



#Gap Statistics

*For computing the gap statistics method we can utilize the clusGap function for providing gap statistic as well as standard error for a given output.


```{r}
library(NbClust)
library(cluster)
```

```{r}
set.seed(125)
stat_gap <- clusGap(dataset,FUN=kmeans,nstart=25,K.max = 10,B=50)
fviz_gap_stat(stat_gap)
```

```{r}
View(dataset)
```

```{r}
clusterK <- kmeans(dataset,10,iter.max = 100,nstart = 50,algorithm = "Lloyd")
clusterK
```

```{r}
pclust <- prcomp(dataset,scale. = FALSE)
summary(pclust)
```

```{r}
pclust$rotation[,1:2]
```

```{r}
kCols=function(vec){cols=rainbow (length (unique (vec)))
return (cols[as.numeric(as.factor(vec))])}
digCluster <- clusterK$cluster 
dignm <- as.character(digCluster)
plot(pclust$x[,1:2],col=kCols(digCluster),pch=19,xlab = "K-Means",ylab = "Classes")
legend("bottomleft",unique(dignm),fill = unique(kCols(digCluster)))
```


